Article Title

### 2013-12-17 plos.tex
minor

\section*{Discussion}
\subsection*{Functional connectivity from big neural data}
Transformational breakthroughs in neuroscience are anticipated to follow technological advances that will allow simultaneous recordings of the spiking activity of much larger subsets of neurons in functioning neural circuits than have been possible thus far. It far from certain whether massively multineuronal recordings will readily reveal new principles of neural function by application of current statistical techniques. Most common analyses of the functional connectivity rely on analyzing pairwise correlation coefficients, t-tests, ANCOVA, principal component analysis of correlated activity, and cross-correlations.  Traditionally, functional connectivity between regions has been defined as the level of correlation or synchronization between regions or cells. Without targeted stimulation and intracellular signals, synaptic connectivity could be inferred with some degree of confidence from the presence of sharp peaks or troughs in the cross-correlograms at offsets corresponding to typical synaptic transmission delays. However, even such effects can be explained by multiple effects besides monosynaptic connections while some strong synaptic connections do not necessarily produce a clear spike in the cross-correlogram. The situations is a bit more complicated in recording modalities, such as calcium imaging, in which only firing rates at lower temporal resolutions can be inferred and cross-correlograms with millisecond precision cannot be obtained. Therefore, some researchers have resorted to using simple correlations as proxies of functional connectivity. Yet, correlations are the end product of multiple cell interactions and, which do not always correspond to

>>>>

\section*{Discussion}
\subsection*{Functional connectivity from big neural data}
Transformational breakthroughs in neuroscience are anticipated to follow technological advances that will allow simultaneous recordings of the spiking activity of much larger subsets of neurons in functioning neural circuits than have been possible thus far. It far from certain whether massively multineuronal recordings will readily reveal new principles of neural function by application of current statistical techniques. Most common analyses of the functional connectivity rely on analyzing pairwise correlation coefficients, t-tests, ANCOVA, principal component analysis of correlated activity, and cross-correlations.  Traditionally, functional connectivity between regions has been defined as the level of correlation or synchronization between regions or cells. Without targeted stimulation and intracellular signals, synaptic connectivity could be inferred with some degree of confidence from the presence of sharp peaks or troughs in the cross-correlograms at offsets corresponding to typical synaptic transmission delays. However, even such effects can be explained by multiple effects besides monosynaptic connections while some strong synaptic connections do not necessarily produce a clear spike in the cross-correlogram. The situations is a bit more complicated in recording modalities, such as calcium imaging, in which only firing rates at lower temporal resolutions can be inferred and cross-correlograms with millisecond precision cannot be obtained. Several studies have used sample correlations to infer graphs of functional connectivities. Yet, correlations are the end product of multiple cell interactions and, which do not always correspond to

Increasingly, functional connectivity is inferred by fitting probabilistic models such as Generalized Linear Models \cite{Pillow:2008} or Ising Models \cite{Schneidman:2006,Tkacik:2006,Tang:2008,Shlens:2009}. In probabilistic models, functional dependencies correspond to terms in the model. If two neurons do not participate in single term in the model, they are conditionally independent: the activity of one of the two neurons can be predicted from other neurons just as well with or without the second neuron.
